Democratizing Secure Two-Party Computation

### 2017-10-15 OaklandSubmission/related.tex
more commits to related work section.

%\end{enumerate}
\nc{First pass of the related work.}\\
\nc{ABY have a list of papers that combine boolean and arithmetic compute (hand crafted protocols). We can cite them in the intro or somewhere else to say all those can be automated.}

@@

Other low level implementations of secure computation protocols look to optimize circuits for depth (such as~\cite{ddkssz15}) or provide protocols for MIPS code~\cite{mips} using techniques from ORAM to hide access patterns~\cite{oram1,oram2}.
\\\\
\noindent\textbf{Custom SMC protocols.}

\nc{Need to write this.}

\begin{enumerate}

\item ML prediction: Minionn, Shafi paper, David Wu paper

\end{enumerate}

>>>>

%\end{enumerate}

@@

Other low level implementations of secure computation protocols look to optimize circuits for depth (such as~\cite{ddkssz15}) or provide protocols for MIPS code~\cite{mips} using techniques from ORAM to hide access patterns~\cite{oram1,oram2}.
\\\\
\noindent\textbf{Custom SMC protocols.} Many works have designed specialized, hand-crafted protocols for various secure two-party computation tasks. The reason for doing this was to allow for a mix between arithmetic and boolean computations as a secure computation protocol for a pure boolean circuit would have been very inefficient. Such hand-crafting of protocols require deep cryptography know-how of designing secure computation protocols with various tools such as homomorphic encryption, garbled circuits, oblivious transfer and so on. A sample of such work includes various works on privacy-preserving classification of medical ElectroCardioGram (ECG)~\cite{ecgclassifier}, iris and fingerprint recognition~\cite{irisfingerprint}, remote diagnostics~\cite{remotediagnostics}, private sequence analysis~\cite{sequenceanalysis}, private biometric identification~\cite{biometricidentification}, privacy-preserving matrix factorization and ridge-regression~\cite{matrixfactorization, ridgeregression}, machine-learning classification~\cite{shafindss}, decision trees and forests~\cite{wu}, neural network training and prediction~\cite{secureml,minionn}. As seen from our experiments, the protocols generated by \tool give us comparable execution times as many of the above works with minimal programmer overhead. \nc{What do we want to say here exactly?}
